### 2017-11-07 poster/poster.tex
last minute formatting, additions, phrasing, typos

\usepackage{multicol} % This is so we can have multiple columns of text side-by-side
\columnsep=100pt % This is the amount of white space between the columns in the poster
\columnseprule=3pt % This is the thickness of the black line between the columns in the poster
%\raggedcolumns

@@

\huge \textbf{Yoav Ram$^{1,a}$, Uri Liberman$^{2}$, and Marcus W. Feldman$^1$}\\ % Author(s)

@@

\Large $^{a}$ Postdoctoral fellow of the Stanford Center for Computational, Evolutionary and Human Genomics

@@

\vspace{4cm} % A bit of extra whitespace between the header and poster content

@@

Examples include social learning in humans, birds, and mammals, pathogen andsymbiont transmission, and HGT in microbes.

@@

We model an infinite population with two phenotype -- $A$ and $B$ -- with frequencies $x$ and $1-x$ and fitnesses $w_A$ and $w_B$.

Offspring inherit its phenotype from its parent with probability $\rho$ or from a random adult with probability $1-\rho$.

The frequency of $A$ in the next generation $x'$ is given by
\begin{equation}
x' = \rho \frac{w_A}{\bar{w}}x + (1-\rho) x
\end{equation}

We consider an environmental regime $AkBl$ which favors phenotype $A$ for $k$ generations and then phenotypes $B$ for $l$ generations.
Let $W$ be the fitness of the favored phenotype and $w$ be that of the other phenotype where $0<w<W$.

@@

\section*{Phenotype dynamics: $AkBl$}

\paragraph*{Result 1.}\textit{Fixation of both $A$ and $B$ is unstable if
\begin{equation}
\frac{\log a}{\log(b)} < \frac{l}{k} < \frac{\log(b)}{\log a}.
\end{equation} 
Specifically, if $k=l$ then there is a protected polymorphism.}

\begin{center}\vspace{1cm}
\includegraphics[width=0.8\linewidth]{lk_phase_plane_F}
\captionof{figure}{Oblique transmission maintains polymorphism.}
\end{center}\vspace{1cm}

@@

\section*{Phenotype dynamics: $A1B1$}

\paragraph*{Result 2.}\textit{In the case $A1B1$ with there exists a unique stable polymorphism:
\begin{equation}
x^* =\frac{1}{2} -\frac{W+w-\sqrt{\left(1-\rho\right)^2\left(W-w\right)^2 +4Ww}}{2\cdot(2-\rho)(W-w)}.
\end{equation}
}

\begin{center}\vspace{1cm}
\includegraphics[width=0.8\linewidth]{A1B1_equilibrium_B}
\captionof{figure}{In $A1B1$ selection regime, the stable population mean fitness decrease as $\rho$ increases.
}
\end{center}\vspace{1cm}

@@

Consider a modifier locus with alleles $m/M$ that determines the vertical transmission rates $\rho/P$:
\begin{equation}
\begin{matrix}
 \text{ pheno-genotype}&mA&mB&MA&MB\\
 \text{ frequency}&x_1&x_2&x_3&x_4\\
 \text{ fitness}&w_A&w_B&w_A&w_B\\
 \text{ vertical transmission rate}&\rho&\rho&P&P\\
\end{matrix}
\end{equation}

The next generation pheno-genotype frequencies are
\begin{equation}
\begin{aligned}
\hat{w}x'_1 &= w_A x_1\bigl[(1-\rho)(x_1+x_3) +\rho\bigr] +w_B x_2(1-\rho)(x_1+x_3)\\
\hat{w}x'_2 &= w_A x_1(1-\rho)(x_2+x_4) +w_B x_2\bigl[(1-\rho)(x_2+x_4)+\rho\bigr]\\ 
\hat{w}x'_3 &= w_A x_3\bigl[(1-P)(x_1+x_3) +P\bigr] +w_B x_4(1-P)(x_1+x_3)\\
\hat{w}x'_4 &= w_A x_3(1-P)(x_2+x_4) +w_B x_4\bigl[(1-P)(x_2+x_4)+P\bigr], 
\end{aligned}
\end{equation}

\paragraph{Evolutionary stable vertical transmission rate.}
We start with a single modifier $m$ with rate $\rho$ at equilibrium between phenotypes $A$ and $B$, and then introduce modifier $M$ with rate $P$ at a low frequency.
If $m$ is stable to invasion of every $M$ with any rate $P$, then we declare $\rho$ to be the stable rate $\rho^*$.

@@

\section*{Modifier dynamics: $A1B1$}

\paragraph*{Result 3.}\textit{In $A1B1$ selection regime, a modifier allele $m$ producing vertical transmission rate $\rho$ is stable to the introduction of a modifier allele $M$ with associated rate $P$ if $P>\rho$, and it is unstable if $P<\rho$.
}

Similar dynamics were observed in environments which randomly flip between $A$ and $B$ every generation.

\begin{center}\vspace{1cm}
\includegraphics[width=0.8\linewidth]{A1B1_modifier_invasions}
\captionof{figure}{In $A1B1$ selection regime, modifier alleles that reduce the vertical transmission rate successfully invade and fix in the population.
}
\end{center}\vspace{1cm}

@@

\section*{Modifier dynamics: $AkBl$}

@@

\begin{center}\vspace{1cm}
\includegraphics[width=0.8\linewidth]{AkBk_stable_optimal_rate}
\captionof{figure}{The evolutionary stable vertical transmission rate $\rho^*$ and the transmission rate $\hat{\rho}$ that maximized the geometric average of the population mean fitness over $k+l$ generations are only the same for $k=l=1$ and $k=l=2$.
}
\end{center}\vspace{1cm}

For $k \ne l$, there is a polymorphism between $A$ and $B$ for $w=0.1$ (but not $w=0.5$ or $0.9$), in which case the stable and optimal rates given in the table.

\begin{center}\vspace{1cm}
\begin{tabular}{p{2.5cm} p{2.5cm} p{4.5cm} p{4.5cm}}
\toprule
\textbf{$k$} & \textbf{$l$ } & \textbf{$\hat{\rho}$} & \textbf{$\rho^*$} \\
\midrule
1 & 2 & 0.00065 & 0.821 \\
3 & 10 & 0.00031 & 0.619 \\
5 & 30 & 0.00027 & 0.6503 \\
\bottomrule
\end{tabular}
\captionof{table}{Values of $\rho^*$ (stable rate) and $\hat\rho$ (fitness optimal rate) in $AkBl$ selection regime.}
\end{center}\vspace{1cm}

>>>>

\usepackage{multicol} % This is so we can have multiple columns of text side-by-side
\columnsep=100pt % This is the amount of white space between the columns in the poster
\columnseprule=3pt % This is the thickness of the black line between the columns in the poster
%\raggedcolumns
\usepackage{fontawesome}

@@

\huge \textbf{Yoav Ram$^{1}$, Uri Liberman$^{2}$, and Marcus W. Feldman$^1$}\\ % Author(s)

@@

%\vspace{1cm}

\Large YR is a postdoctoral fellow of the Stanford Center for Computational, Evolutionary and Human Genomics\\ 
\faicon{envelope-o}\; yoav@yoavram.com \quad
\faicon{phone}\; 650.440.9625 \quad
\faicon{globe}\; www.yoavram.com

@@

\vspace{2cm} % A bit of extra whitespace between the header and poster content

@@

Examples include social learning in humans, birds, and mammals, pathogen and symbiont transmission, and HGT in microbes.

@@

We model an infinite population with two phenotype, $A$ and $B$, with frequencies $x$ and $1-x$.
An offspring inherits its phenotype from its parent with probability $\rho$ or from a random adult with probability $1-\rho$.

We consider an environmental regime $AkBl$ which favors phenotype $A$ for $k$ generations and then phenotype $B$ for $l$ generations.
Let $W$ be the fitness of the favored phenotype and $w$ be that of the other phenotype where $0<w<W$.

The frequency of $A$ in the next generation $x'$, when $A$ is \mbox{favored} over $B$, is given by
\begin{equation}
x' = \rho \frac{W}{\bar{w}}x + (1-\rho) x
\end{equation}
where $\bar{w}=xW + (1-x)w$ is the population mean fitness.

@@

\section*{Phenotype dynamics: \emph{AkBl}}

\paragraph*{Result 1.}\textit{Fixation of both $A$ and $B$ is unstable if
\begin{equation}
\frac{\log(1+\rho \frac{W-w}{w})}{\log(1+\rho \frac{w-W}{W})} < 
\frac{l}{k} <
\frac{\log(1+\rho \frac{w-W}{W})}{\log(1+\rho \frac{W-w}{w})}.
\end{equation} 
Specifically, if $k=l$ then there is a protected polymorphism.}

\begin{center}\vspace{1cm}
\includegraphics[width=0.8\linewidth]{lk_phase_plane_F}
\captionof{figure}{\textbf{Oblique transmission maintains polymorphism.}}
\end{center}\vspace{1cm}

@@

\section*{Phenotype dynamics: \emph{A1B1}}

\paragraph*{Result 2.}\textit{In selection regime $A1B1$ there exists a unique stable polymorphism:
\begin{equation}
x^* =\frac{1}{2} -\frac{W+w-\sqrt{\left(1-\rho\right)^2\left(W-w\right)^2 +4Ww}}{2\cdot(2-\rho)(W-w)},
\end{equation}
where $x^*$ is the stable frequency of phenotype $A$ after the end of each two-generation cycle.
}

Since $\bar{w}^*$ is a decreasing function function of $x^*$, the stable population mean fitness $\bar{w}^*$ is a decreasing function of $\rho$.

\begin{center}\vspace{1cm}
\includegraphics[width=0.8\linewidth]{A1B1_equilibrium_B}
\captionof{figure}{\textbf{Mean fitness in A1B1 selection regime}.
The stable population mean fitness $\bar{w}^*$ decreases as the vertical transmission rate $\rho$ increases.
}
\end{center}\vspace{1cm}

@@

Consider a modifier locus with alleles $m/M$ that determine the vertical transmission rates $\rho/P$:
\begin{equation}
\begin{matrix}
 \text{ pheno-genotype}&mA&mB&MA&MB\\
 \text{ frequency}&x_1&x_2&x_3&x_4\\
 \text{ fitness when $A$ is favored}&W&w&W&w\\
 \text{ fitness when $B$ is favored}&w&W&w&W\\
 \text{ vertical transmission rate}&\rho&\rho&P&P\\
\end{matrix}
\end{equation}

The next generation pheno-genotype frequencies when $A$ is favored are
\begin{equation}
\begin{aligned}
\hat{w}x'_1 &= W x_1\bigl[(1-\rho)(x_1+x_3) +\rho\bigr] + w x_2(1-\rho)(x_1+x_3)\\
\hat{w}x'_2 &= W x_1(1-\rho)(x_2+x_4) + w x_2\bigl[(1-\rho)(x_2+x_4)+\rho\bigr]\\ 
\hat{w}x'_3 &= W x_3\bigl[(1-P)(x_1+x_3) +P\bigr] + w x_4(1-P)(x_1+x_3)\\
\hat{w}x'_4 &= W x_3(1-P)(x_2+x_4) + w x_4\bigl[(1-P)(x_2+x_4)+P\bigr], 
\end{aligned}
\end{equation}

\paragraph{Evolutionary stable vertical transmission rate.}
We start with modifier allele $m$ with rate $\rho$ at equilibrium between phenotypes $A$ and $B$, and then introduce modifier allele $M$ with rate $P$ at a low frequency.
If $m$ is stable to invasion of any $M$ with any rate $P$, then we declare $\rho$ to be the stable rate $\rho^*$.

@@

\section*{Modifier dynamics: \emph{A1B1}}

\paragraph*{Result 3.}\textit{In selection regime $A1B1$, a modifier allele $m$ with associated vertical transmission rate $\rho$ is stable to the introduction of a modifier allele $M$ with associated rate $P$ if $P>\rho$, and it is unstable if $P<\rho$.
}

That is, there is a \emph{reduction principle} for the vertical transmission rate in selection regime $A1B1$.

Similar dynamics were observed in environments which randomly flip between favoring $A$ and $B$ every generation.

\begin{center}\vspace{1cm}
\includegraphics[width=0.8\linewidth]{A1B1_modifier_invasions}
\captionof{figure}{\textbf{Modifier invasion in A1B1 selection regime}.
Modifier alleles that reduce the vertical transmission rate successfully invade and fix in the population.
Dashed lines show invasion times. Initial resident allele with $\rho=0.1$.
}
\end{center}\vspace{1cm}

@@

\section*{Modifier dynamics: \emph{AkBk}}

@@

\begin{center}\vspace{1cm}
\includegraphics[width=0.8\linewidth]{AkBk_stable_optimal_rate}
\captionof{figure}{\textbf{Stability and optimality in selection regime $AkBk$.} \textbf{(A)} The transmission rate $\hat{\rho}$ that maximizes the geometric average of the population mean fitness over $k+l$ generations, and \textbf{(B)} the evolutionary stable vertical transmission rate $\rho^*$.
$\rho^*$ and $\hat{\rho}$ are equal to 0 and to each other only when $k=l=1$ and $k=l=2$.
}
\end{center}\vspace{1cm}

\section*{Modifier dynamics: \emph{AkBl}}

For $k \ne l$, there is a polymorphism between $A$ and $B$ when $w=0.1$ (but not when $w=0.5$ or $0.9$), in which case the stable and optimal rates are given below.

\begin{center}\vspace{1cm}
\begin{tabular}{p{2.5cm} p{2.5cm} p{4.5cm} p{4.5cm}}
\toprule
\textbf{$k$} & \textbf{$l$ } & \textbf{$\hat{\rho}$} & \textbf{$\rho^*$} \\
\midrule
1 & 2 & 0.00065 & 0.821 \\
3 & 10 & 0.00031 & 0.619 \\
5 & 30 & 0.00027 & 0.6503 \\
\bottomrule
\end{tabular}
\captionof{table}{\textbf{Stability and optimality in selection regime AkBl.}
Values of evolutionary stable vertical transmission rate $\rho^*$ and the transmission rate $\hat\rho$ that maximizes geometric mean fitness.}
\label{table}
\end{center}%\vspace{1cm}
